This chapter describes how events in data and simulated samples are selected in the search for $h \rightarrow aa \rightarrow bb\tau\tau$. The event selection is motivated by optimization checks aimed at maximizing the final expected limit, and is also based on recommendations from CMS Physics Objects Groups. As described in the previous chapter, the tau lepton can decay to electrons ($e$), muons ($\mu$), or hadronic states ($\tau_{h}$). As a result, several different final states of the $\tau\tau$ system are possible, and are here referred to as ``channels" since they are mutually exclusive. The three $\tau\tau$ final states studied in this analysis are muon and hadronic tau ($\mu\tau_{h}$), electron and hadronic tau ($e\tau_{h}$), and electron and muon ($e\mu$). The procedure for dividing events into these three channels begins with checking the High-Level Trigger paths passed by the events as detailed in Section \ref{section:general_event_selection}. Events are further accepted or rejected based on criteria applied to the leptons in the event. These event selections are described for the $\mu\tau_{h}$ channel in Section \ref{section:ch-6-event-selection-mutau}, the $e\tau_{h}$ channel in Section \ref{section:ch-6-event-selection-etau}, and the $e\mu$ channel in Section \ref{section:ch-6-event-selection-emu}.


\section{General procedure for all channels}
\label{section:general_event_selection}
For the search for $h \rightarrow aa \rightarrow bb\tau\tau$, three final states of the $\tau\tau$ system are considered: $\mu\tau_{h}$, $e\tau_{h}$, and $e\mu$. The $\tau_{h}\tau_{h}$ final state is not considered because signal events in the $\tau_{h}\tau_{h}$ channel would typically produce hadronic taus with momenta below data-taking trigger thresholds. In all three final states, events are required to have at least one b-tag jet passing the medium working point of the DeepFlavour tagger, with $p_{T} > 20$ GeV, and $|\eta| < 2.4$. A second b-tag jet is not required because such a requirement would reduce signal acceptance by 80\% compared to only requiring one b-tag jet.

Events in MC samples are sorted into one of the three $\tau\tau$ channels if they pass the following trigger requirements and requirements on the offline reconstructed objects in the event, first checking the HLT paths for the $\mu\tau_{h}$ channel, then $e\tau_{h}$, and finally $e\mu$. The two leading leptons (e.g. muon and hadronic tau for the $\mu\tau_{h}$ channel) that were determined to have originated from the $\tau\tau$ decay, are called the $\tau\tau$ ``legs''. For events in data and embedded samples, the HLT path requirements for the corresponding channel are checked.

After sorting events by HLT paths and identifying the leading tau legs in the offline reconstructed objects, the $p_{T}$ of the offline objects is checked against the online trigger thresholds. Trigger matching is also performed, which checks the correspondence between each offline reconstructed object used in the analysis (e.g. a muon), and a trigger object in the HLT (e.g. a HLT muon). An offline object is considered to be matched, if it corresponds to a trigger object of the same object type, with $\Delta R < 0.5$. This matched trigger object is also required to pass the filter(s) of the HLT trigger. The trigger thresholds used for the $bb\mu\mu$ final state and the $bb\tau\tau$ final state (the focus of this work) are summarized in Tables \ref{tab:trigger_thresholds}.

After checking the HLT paths and trigger objects in each channel, events are subject to further selection to ensure that they contain leptons and b-tag jet(s) of interest. These requirements are summarized in Table \ref{table:object_selections}, and detailed in the following sections. 

\begin{table}[ht!]
    \centering
    \begin{tabular}{|lc|c|cccccc|}
    \hline
    \multirow{3}{*}{ Year } & \multirow{3}{*}{ Single/dilepton trigger $p_{T}$ } & $bb\mu\mu$ & \multicolumn{6}{c|}{$bb\tau\tau$} \\
    & & & \multicolumn{2}{c}{$e\mu$} & \multicolumn{2}{c}{$e\tau_{h}$} & \multicolumn{2}{c|}{$\mu\tau_{h}$}  \\
    & & $\mu$ & $e$ & $\mu$ & $e$ & $\tau_{h}$ & $\mu$ & $\tau_{h}$ \\
    \hline
    \multirow{3}{*}{ 2016 } & Single lepton      &  24     &        \textendash       &       \textendash      &         25          &          \textendash         &          22         &         \textendash    \\
                            & $p_{T}$-leading lepton        &  17     &        23       &       23      & \multirow{2}{*}{\textendash} & \multirow{2}{*}{\textendash} &          \textendash         &         20    \\
                            & $p_{T}$-subleading lepton     &  8      &        12       &       8       &                     &                     &          19         &         \textendash    \\
    \hline
    \multirow{3}{*}{ 2017 } & Single lepton       & 24      &        \textendash       &       \textendash      &       27, 32        &          \textendash         &       24, 27        &         \textendash    \\
                            & $p_{T}$-leading lepton        &  17     &        23       &       23      &         \textendash          &          30         &          \textendash         &         27    \\
                            & $p_{T}$-subleading lepton     &  8      &        12       &       8       &         24          &          \textendash         &          20         &         \textendash    \\
    \hline
    \multirow{3}{*}{ 2018 } & Single lepton      & 24      &        \textendash       &       \textendash      &       32, 35        &          \textendash         &       24, 27        &         \textendash    \\
                            & $p_{T}$-leading lepton        &  17     &        23       &       23      &         \textendash          &          30         &          \textendash         &         27    \\
                            & $p_{T}$ subleading lepton     &  8      &        12       &       8       &         24          &          \textendash         &          20         &         \textendash    \\
    \hline
    \end{tabular}
    \caption{Trigger thresholds used for the leptons in the $bb\mu\mu$ analysis and the $bb\tau\tau$ analysis (the focus of this work). The thresholds for the three $bb\tau\tau$ channels ($e\mu$, $e\tau_{h}$, and $\mu\tau_{h}$) are listed separately, with some channels and years taking the logical OR of two triggers with different thresholds.}
    \label{tab:trigger_thresholds}
\end{table}
    
\begin{table}[]
    \begin{tabular}{|ccccc|}
    \hline
    \multicolumn{5}{|c|}{All years (2016, 2017, 2018) and eras}                                                                                 \\ \hline
    \multicolumn{1}{|c|}{\multirow{2}{*}{Kinematic variable}}   & \multicolumn{1}{c|}{$bb\mu\mu$} & \multicolumn{3}{c|}{$bb\tau\tau$}           \\
    \multicolumn{1}{|c|}{}                                      & \multicolumn{1}{c|}{$\mu$}      & $e\mu$    & $e\tau_{h}$    & $\mu\tau_{h}$  \\ \hline
    \multicolumn{1}{|c|}{$\Delta R$ between leptons}            & \multicolumn{1}{c|}{$>$0.4}     & $>$0.3    & $>$0.4         & $>$0.4         \\
    \multicolumn{1}{|c|}{$|\eta|$ of electron}                  & \multicolumn{1}{c|}{-}          & $<$2.4    & $<$2.1         & -              \\
    \multicolumn{1}{|c|}{$|\eta|$ of muon}                      & \multicolumn{1}{c|}{$<$2.4}     & $<$2.4    & -              & $<$2.1         \\
    \multicolumn{1}{|c|}{$|\eta|$ of hadronic tau}              & \multicolumn{1}{c|}{-}          & -         & $<$2.3/$<$ 2.1 & $<$2.3/$<$ 2.1 \\
    \multicolumn{1}{|c|}{Relative isolation of electron}        & \multicolumn{1}{c|}{-}          & $<$0.10   & -              & $<$0.15        \\
    \multicolumn{1}{|c|}{Relative isolation of muon}            & \multicolumn{1}{c|}{$<$0.25}    & $<$0.15   & -              & $<$0.15        \\
    \multicolumn{1}{|c|}{Leading b-tag jet $p_{T}$}             & \multicolumn{1}{c|}{$>$15 GeV}  & \multicolumn{3}{c|}{$>$20 GeV}     \\
    \multicolumn{1}{|c|}{Leading b-tag jet $|\eta|$}            & \multicolumn{1}{c|}{$<$2.4}     & \multicolumn{3}{c|}{$<$2.4}                 \\
    \multicolumn{1}{|c|}{Leading b-tag jet WP}                  & \multicolumn{1}{c|}{Tight}      & \multicolumn{3}{c|}{Medium}                 \\
    \multicolumn{1}{|c|}{Sub-leading b-tag jet $p_{T}$}         & \multicolumn{1}{l|}{$>$15 GeV}  & \multicolumn{3}{c|}{-}                      \\
    \multicolumn{1}{|c|}{Sub-leading b-tag jet $|\eta|$}        & \multicolumn{1}{c|}{$<$2.4}     & \multicolumn{3}{c|}{-}                      \\
    \multicolumn{1}{|c|}{Sub-leading b-tag jet WP}              & \multicolumn{1}{c|}{Loose}      & \multicolumn{3}{c|}{-}                      \\
    \multicolumn{1}{|c|}{$\Delta R$ between jet(s) and leptons} & \multicolumn{1}{c|}{$>$0.4}     & \multicolumn{3}{c|}{$>$0.5}                 \\ \hline
    \end{tabular}
    \caption{Summary of requirements applied to the leptons in the $bb\mu\mu$ analysis and the $bb\tau\tau$ analysis (the focus of this work). $\Delta R = \sqrt{(\Delta \eta)^2 + (\Delta \phi)^2}$ is a measure of spatial separation. Relative isolation is defined in Eqn. \ref{eqn:definition-relative-isolation} and Section \ref{section:ch-5-muon-reconstruction}. The b-tag jets are required to pass the listed DeepFlavour working points (WP), which are described in Section \ref{section:b-flavour-jets}. In the $bb\tau\tau$ analysis, the required $|\eta|$ of the hadronic taus are listed for the single and cross triggers respectively. The $bb\mu\mu$ analysis requires two b-tag jets in all events, while the $bb\tau\tau$ analysis only requires one.}
    \label{table:object_selections}
\end{table}

\section{Event selection in the \texorpdfstring{$\mu\tau_{h}$}{mutauh} channel}
\label{section:ch-6-event-selection-mutau}
In all three years, a single muon trigger is used if the muon has sufficiently high $p_{T}$, otherwise a dilepton $\mu\tau_{h}$ cross-trigger is used (Tables \ref{table:trigger2016}, \ref{table:trigger2017}, and \ref{table:trigger2018}). For data taken in 2017-2018 (2016), the logical OR of the single muon triggers with online $p_{T}$ thresholds 24 and 27 (23) GeV is used, with the corresponding offline muon required to have with $p_{T}$ 1 GeV above the online threshold. For data taken in 2017-2018 (2016), a dilepton $\mu + \tau_{h}$ cross-trigger with $p_{T}$ thresholds of 20 (19) and 27 (20) GeV for the muon and tau respectively, is used. The $\tau_{h}$ is required to have $|\eta| < 2.3$ if the single trigger is fired, $|\eta| < 2.1$. 

The muon and $\tau_h$ are required to have opposite charges and be separated by $\Delta R > 0.4$. The muon is required to have $|\eta| < 2.4$, and the $\tau_{h}$ is required to have $|\eta| < 2.3$ unless a cross-trigger is required, in which case we require $|\eta| < 2.1$ as discussed above.

The muon is required to pass the medium identification (ID) working point~\cite{twiki_MUON_POG_Run2_guide}, which is defined by the Muon POG as a loose muon (i.e. a Particle Flow muon that is either a global or a tracker muon - see Section \ref{section:ch-5-muon-reconstruction}) with additional requirements on track quality and muon quality. These identification criteria are designed to be highly efficient for prompt muons and for muons from heavy quark decays. In addition to the ID, for prompt muons it is recommended to apply cuts on the impact parameter~\cite{twiki_MUON_POG_Run2_guide}: we apply $|\Delta(z)| < 0.2$ and $|\Delta(xy)| < 0.045$. A cut is applied on the muon relative isolation (defined in Section \ref{section:ch-5-muon-reconstruction}), to be less than 0.15 in a cone size of $\Delta R = 0.4$, which corresponds to the Tight Particle Flow isolation requirement~\cite{twiki_MUON_POG_Run2_guide}.

The $\tau_h$ is required to pass a cut on its impact parameter of $|\Delta(z)| < 0.2$. The $\tau_h$ is also required to pass the VLoose (Very Loose) DeepTau working point vs. electron, the Tight DeepTau working point vs. muons, and the VVVLoose and Medium DeepTau working point vs. jets. Events with taus reconstructed in two of the decay modes (labeled 5 and 6) are rejected, since these decay modes are meant to recover 3-prong taus, but are only recommended for use in analyses where the benefits in final significance outweigh the resulting increase in background~\cite{twiki_TAU_POG_tauidrecommendationforrun2}. Decays reconstructed with 2 prongs are not considered as they are only recommended for taus with a very high transverse momentum, where the prongs may overlap.

For the estimation of the background from jets faking $\tau_{h}$, which is described in Section \ref{section:ch-7-jet-faking-tauh-background}, anti-isolated events are selected, by requiring events to pass all the selections described above, except failing the Medium DeepTau working point vs. jets.

\section{Event selection in the \texorpdfstring{$e\tau_{h}$}{etauh} channel}
\label{section:ch-6-event-selection-etau}

The HLT trigger paths for the $e\tau_{h}$ channel are summarized in Tables \ref{table:trigger2016}, \ref{table:trigger2017}, and \ref{table:trigger2018}. Similarly to the $\mu\tau_{h}$ channel, a single electron trigger is used if the electron has sufficiently high $p_{T}$ in 2018 and 2017. For data taken in 2018 (2017), the OR of the single electron triggers with online $p_{T}$ thresholds at 32 and 35 (27 and 32) GeV are used, with the corresponding offline electrons required to have $p_{T}$ greater than 33 (28) GeV. A $e + \tau_{h}$ cross-trigger is used for electrons with lower offline $p_{T}$ between 25 and 33 GeV (25 and 28 GeV). For the 2016 dataset, there is no cross trigger but only a single electron trigger with online $p_{T}$ threshold at 25 GeV, which is used if the offline electron has $p_{T}$ greater than 26 GeV.

The electron and $\tau_h$ are required to have opposite charges and be separated by $\Delta R > 0.4$. The electron is required to be within $|\eta| < 2.3$ when no cross trigger is used, and $|\eta| < 2.1$ when the cross trigger is fired. The $\tau_{h}$ is required to have $|\eta| < 2.3$ if no cross trigger is fired, and have $|\eta| < 2.1$ if the cross trigger is fired.

The electron is required to have a relative isolation (same definition as in Section \ref{section:ch-5-muon-reconstruction}) of less than 0.1 in a cone size of $\Delta R = 0.3$, which is the standard recommended cone size giving minimal pile-up dependence and reduced probability of other objects overlapping with the cone. The isolation quantity used includes an ``effective area'' (EA) correction to remove the effect of pile-up in the barrel and endcap parts of the detector~\cite{twiki_EGamma_cutbased_ID_info}. The electron is also required to pass cuts on its impact parameter of $|\Delta(z)| < 0.2$ and $|\Delta(xy)| < 0.045$. It is also required to pass the non-isolated MVA working point corresponding to 90\% efficiency. The electron's number of missing hits, which are gaps in its trajectory through the inner tracker~\cite{twiki_EGamma_cutbased_ID_info}, must be less than or equal to 1. The electron must pass a conversion veto, which rejects electrons coming from photon conversions in the tracker, which should instead be reconstructed as part of the photon~\cite{twiki_EGamma_cutbased_ID_info}.

The impact parameter cut for the $\tau_h$ is $|\Delta(z)| < 0.2$. In contrast to the $\mu\tau_{h}$ event selection, the vs. electron and vs. muon DeepTau working points are flipped, to reject muons faking the $\tau_{h}$ leg. The $\tau_h$ is required to pass the Tight DeepTau working point vs. electrons, the VLoose DeepTau working point vs. muons, and the Medium DeepTau working point vs. jets.

As in the $\mu\tau_{h}$ channel, for the estimation of the background from jets faking $\tau_{h}$, which is described in Section \ref{section:ch-7-jet-faking-tauh-background}, anti-isolated events are selected by requiring events to pass all the selections described above, except failing the Medium DeepTau working point vs. jets.

\section{Event selection in the \texorpdfstring{$e\mu$}{emu} channel}
\label{section:ch-6-event-selection-emu}

The HLT trigger paths for the $e\mu$ channel are summarized in Tables \ref{table:trigger2016}, \ref{table:trigger2017}, and \ref{table:trigger2018}. Events are selected with the logical OR of two $e+\mu$ cross triggers, where either the electron or muon can have larger $p_{T}$: (1) leading electron, where the electron has online $p_{T} > 23$ GeV and the muon has online $p_{T} > 8$ GeV, or (2) leading muon, where the electron has online $p_{T} > 12$ GeV and the muon has online $p_{T}>23$ GeV.

The leading and sub-leading leptons are required to have an offline $p_{T}$ greater than 1 GeV above the online threshold (i.e. $p_{T} > 24$ GeV). If the sub-leading lepton is the electron, the offline $p_{T}$ threshold is 1 GeV above the online threshold ($p_{T} > 13$ GeV), but if it is a muon, the offline $p_{T}$ threshold is required to be at least 5 GeV greater than the online threshold (i.e. $p_T > 13$ GeV). This is because of poor data and simulation agreement for low-$p_T$ muons with $p_T$ between 9 GeV and 13 GeV, and the higher probability of mis-identifying jets as muons at lower $p_{T}$. With no effect on the expected limits, the offline $p_{T}$ threshold for muons is raised to 13 GeV instead of 9 GeV, even though it may lead to a loss in signal acceptance. Both the electron and muon are required to have $|\eta| < 2.4$.

The electron and muon are required to have opposite charges and be separated by $\Delta R > 0.3$ (note the decreased separation requirement compared to the other two channels). The electron is required to pass the non-isolated MVA identification working point corresponding to 90\% efficiency, and to have a relative isolation less than 0.1 for a cone size of $\Delta R = 0.3$ with the EA pile-up subtraction correction. The electron must have one or fewer missing hits and pass the conversion veto (both described previously in Section \ref{section:ch-6-event-selection-etau}). 

The muon is required to pass the medium identification working point (described earlier in \ref{section:ch-6-event-selection-mutau}), and to have a relative isolation less than 0.15 for a cone size of $\Delta R = 0.4$. The muon impact parameter is required to have $|\Delta(z)| > 0.2$ and $|\Delta(xy) < 0.045$. 

For the QCD multijet background estimation described in Section \ref{section:ch-7-QCD-multijet-background}, the same-sign region is selected by requiring all the above selections, except the legs are required to have the same electric charge rather than opposite.


\begin{table}[h]
    \centering
    \begin{tabular}{ll}
    \hline
    \multicolumn{2}{|c|}{\footnotesize{2016 $\mu\tau_{h}$ trigger paths}}                                     \\ \hline
    \footnotesize{Notes}          & \footnotesize{HLT Path}                                           \\ \hline
                                  & \footnotesize{HLT\_IsoMu22\_v}                                    \\
                                  & \footnotesize{HLT\_IsoMu22\_eta2p1\_v}                            \\
                                  & \footnotesize{HLT\_IsoTkMu22\_v}                                  \\
                                  & \footnotesize{HLT\_IsoTkMu22\_eta2p1\_v}                          \\
                                  & \footnotesize{HLT\_IsoMu19\_eta2p1\_LooseIsoPFTau20\_v}           \\
                                  & \footnotesize{HLT\_IsoMu19\_eta2p1\_LooseIsoPFTau20\_SingleL1\_v} \\ \hline
    \multicolumn{2}{|c|}{\footnotesize{2016  $e\tau_{h}$ trigger paths}}                                         \\ \hline
    \footnotesize{Notes}          & \footnotesize{HLT Path}                                           \\ \hline
                                  & \footnotesize{HLT\_Ele25\_eta2p1\_WPTight\_Gsf\_v}                \\ \hline
    \multicolumn{2}{|c|}{\footnotesize{2016 $e\mu$ trigger paths}}                                            \\ \hline
    \footnotesize{Notes}           & \footnotesize{HLT Path}                                                     \\ \hline
    \footnotesize{runs B-F and MC} & \footnotesize{HLT\_Mu23\_TrkIsoVVL\_Ele12\_CaloIdL\_TrackIdL\_IsoVL\_v}     \\
    \footnotesize{runs B-F and MC} & \footnotesize{HLT\_Mu8\_TrkIsoVVL\_Ele23\_CaloIdL\_TrackIdL\_IsoVL\_v}      \\
    \footnotesize{runs G-H}        & \footnotesize{HLT\_Mu23\_TrkIsoVVL\_Ele12\_CaloIdL\_TrackIdL\_IsoVL\_DZ\_v} \\
    \footnotesize{runs G-H}        & \footnotesize{HLT\_Mu8\_TrkIsoVVL\_Ele23\_CaloIdL\_TrackIdL\_IsoVL\_DZ\_v} 
    \end{tabular}
    \caption{High-Level Trigger (HLT) paths used to select data and simulation events in 2016 for the three $\tau\tau$ channels.}
    \label{table:trigger2016}
\end{table}

    
\begin{table}[h]
    \centering
    \begin{tabular}{ll}
    \hline  
    \multicolumn{2}{|c|}{\footnotesize{2017 $\mu\tau_{h}$ trigger paths}}                                     \\ \hline
    \footnotesize{Notes}         & \footnotesize{HLT Path}                                                           \\ \hline
                                 & \footnotesize{HLT\_IsoMu24\_v}                                                    \\
                                 & \footnotesize{HLT\_IsoMu27\_v}                                                    \\
                                 & \footnotesize{HLT\_IsoMu20\_eta2p1\_LooseChargedIso\_PFTau27\_eta2p1\_CrossL1\_v} \\ \hline
    \multicolumn{2}{|c|}{\footnotesize{2017  $e\tau_{h}$ trigger paths}}                                         \\ \hline
    \footnotesize{Notes}         & \footnotesize{HLT Path}                                                       \\ \hline
                                 & \footnotesize{HLT\_Ele32\_WPTight\_Gsf\_v}                                                    \\
                                 & \footnotesize{HLT\_Ele35\_WPTight\_Gsf\_v}                                                    \\
                                 & \footnotesize{HLT\_Ele24\_eta2p1\_WPTight\_Gsf\_Loose\_ChargedIsoPFTau30\_eta2p1\_CrossL1\_v} \\ \hline
    \multicolumn{2}{|c|}{\footnotesize{2017 $e\mu$ trigger paths}}                                            \\ \hline
    \footnotesize{Notes}         & \footnotesize{HLT Path}                                                        \\ \hline
                                 & \footnotesize{HLT\_Mu23\_TrkIsoVVL\_Ele12\_CaloIdL\_TrackIdL\_IsoVL\_DZ\_v}    \\
                                 & \footnotesize{HLT\_Mu8\_TrkIsoVVL\_Ele23\_CaloIdL\_TrackIdL\_IsoVL\_DZ\_v}                   
    \end{tabular}
    \caption{High-Level Trigger (HLT) paths used to select data and simulation events in 2017 for the three $\tau\tau$ channels.}
    \label{table:trigger2017}
\end{table}
    
    

\begin{table}[h]
    \centering
    \begin{tabular}{ll}
    \hline
    \multicolumn{2}{|c|}{\footnotesize{2018 $\mu\tau_{h}$ trigger paths}}                                     \\ \hline
    \footnotesize{Notes}          & \footnotesize{HLT Path}                                                   \\ \hline
                                  & \footnotesize{HLT\_IsoMu24\_v}                                                           \\
                                  & \footnotesize{HLT\_IsoMu27\_v}                                                           \\
    \footnotesize{only data run $<$ 317509}      & \footnotesize{HLT\_IsoMu20\_eta2p1\_ (contd.)} \\
                                                 & \footnotesize{LooseChargedIsoPFTauHPS27\_eta2p1\_CrossL1\_v} \\
    \footnotesize{MC and data run $\geq$ 317509} & \footnotesize{HLT\_IsoMu20\_eta2p1\_ (contd.)} \\
                                                 & \footnotesize{LooseChargedIsoPFTauHPS27\_eta2p1\_TightID\_CrossL1\_v}     \\ \hline
    \multicolumn{2}{|c|}{\footnotesize{2018 $e\tau_{h}$ trigger paths}}                                       \\ \hline
    \footnotesize{Notes}          & \footnotesize{HLT Path}                                                   \\ \hline
                                  & \footnotesize{HLT\_Ele32\_WPTight\_Gsf\_v}                                               \\
                                  & \footnotesize{HLT\_Ele35\_WPTight\_Gsf\_v}                                               \\
    \footnotesize{only data run $<$ 317509}      & \footnotesize{HLT\_Ele24\_eta2p1\_WPTight\_Gsf\_ (contd.)} \\
                                                 & \footnotesize{LooseChargedIsoPFTauHPS30\_eta2p1\_CrossL1\_v}          \\
    \footnotesize{MC and data run $\geq$ 317509} & \footnotesize{HLT\_Ele24\_eta2p1\_WPTight\_Gsf\_ (contd.)} \\
                                                 & \footnotesize{LooseChargedIsoPFTauHPS30\_eta2p1\_TightID\_CrossL1\_v} \\ \hline
    \multicolumn{2}{|c|}{\footnotesize{2018 $e\mu$ trigger paths}}                                            \\ \hline
    \footnotesize{Notes}          & \footnotesize{HLT Path}                                                   \\ \hline
                                  & \footnotesize{HLT\_Mu23\_TrkIsoVVL\_Ele12\_CaloIdL\_TrackIdL\_IsoVL\_DZ\_v}              \\
                                  & \footnotesize{HLT\_Mu8\_TrkIsoVVL\_Ele23\_CaloIdL\_TrackIdL\_IsoVL\_DZ\_v}                             
    \end{tabular}
    \caption{High-Level Trigger (HLT) paths used to select data and simulation events in 2018 for the three $\tau\tau$ channels. In 2018 a HLT trigger path using the hadron plus strips (HPS) tau reconstruction algorithm became available.}
    \label{table:trigger2018}
\end{table}



\section{Extra lepton vetoes in all channels}

Events containing a third lepton (electron or muon) that is neither of the leading $\tau\tau$ legs are rejected, and events with di-muons and di-electrons are vetoed, with criteria taken from the Standard Model $H \rightarrow \tau\tau$ working group~\cite{twiki_HiggsToTauTauWorkingLegacyRun2}. These vetoes on extra leptons also ensure orthogonality of events to analyses such as the $bb\mu\mu$ final state, whose results are combined with this $bb\tau\tau$ final state as described in Section \ref{section:combination-procedure-with-bbmumu}.

The event is vetoed if a third electron is found with the following properties: $p_{T} > 10$ GeV, $|\eta| < 2.5$, impact parameter $|\Delta(z)| < 0.2$ and $|\Delta(xy)| < 0.045$, passing non-isolation MVA identification with 90\% efficiency, conversion veto, $\leq 1$ missing hits, and relative isolation $<0.3$ with cone size $\Delta R = 0.3$. The event is also vetoed if a third muon is found with the following properties: $p_{T} > 10$ GeV, $|\eta| < 2.4$, impact parameter $|\Delta(z)| < 0.2$ and $|\Delta(xy)| < 0.045$, medium ID, and isolation $<0.3$ with cone size $\Delta R = 0.4$. 

A di-muon veto is applied, which rejects events containing a pair of muons with opposite charges and separation of $\Delta R > 0.15$, that both pass the following selections: $p_T > 15$ GeV, $|\eta| < 2.4$, flag for global muons, flag for tracker muon, flag for Particle Flow muon, $|\Delta(z)| < 0.2$, $|\Delta(xy)| < 0.045$, and isolation $<0.3$ with cone size $\Delta R = 0.4$. A similar di-electron veto is applied to reject events containing a pair of electrons with opposite charges and separation of $\Delta R > 0.15$, that both pass the following selections: $p_T > 15$ GeV, $|\eta| < 2.5$, a dedicated electron ID (cut-based) for vetoing third leptons, $|\Delta(z)| < 0.2$, $|\Delta(xy)| < 0.045$, with pile-up corrected relative isolation $<0.3$ with cone size $\Delta R = 0.3$.
